\section{Introduction}
\label{sec:intro}

As the demand for data collection and the need for data analytic tools
and algorithms that operate on large data grows, we find existing solutions
are not flexible or robust enough to satisfy the needs of data analysts. 
To address this growing demand, we designed a data analytics cloud platform
and implemented a data analysis engine. More specifically our platform provides
generic support for data analysis engines of any type and we used this
platform to implement a data analysis engine that crawls the web for
unstructured data, structures and combines data, then visualizes the
structured data. This data analysis engine demonstrates the potential
power and flexibility of our data analytics cloud platform.

Our project considers a user focused on the development of novel and
computationally intensive algorithms that operate on large data sets.
These data sets vary a wide range of industry use cases, such as Insurance
Services data, Financial Services data, Character Recognition data, 
pharmaceutical data, and much more. To develop algorithms that work on data
sets as described above, as well as other data sets, the user needs a
flexible analytic cloud platform offering both Platform as a Service
(PaaS) and Software as a Service (SaaS) packages.

This document serves as a record for the designing, implementing, and
testing of a custom data analytics cloud platform and data analysis engine. 
The rest of this section describes the project at a high level,
including the problem statement (\ref{sec:problem}) and motivation
(\ref{sec:motivation}), as well as issues encountered when designing
custom data analytic platforms (\ref{sec:issues}), and finally, describes
the environment the platform will be implemented on
(\ref{sec:environment}).

The remaining sections of this document go into details about the
requirements, specific details about the system environment, the design and
implementation of the platform, the testing plan and the results of the
tests, and finally the work schedule and distribution of tasks among the
team members. Any additional information that does not fall into these
sections is then placed within an Appendix at the end.

\input{intro/prob}
\input{intro/motiv}
\input{intro/issues}
\input{intro/environment}
