\subsection{Issues}
\label{sec:issues}
The design of a data analytics platform to provide a solution to the
problem presented in Section~\ref{sec:problem} must address many issues.
The following list identifies the major issues and briefly discusses
why the issues are important. Details about how the issues are 
addressed by our system are covered in Section~\ref{sec:design}.  

\begin{enumerate}
  \item \textbf{Security}

    When a consumer transitions to the cloud, they effectively give
control of their data to a trusted entity. That trusted entity, the
cloud provider, must be able to make guarantees about the security of their
customers data. For example, who can access or change data, who
has accessed or changed data, how was data changed, etc. Security is a
large task not to be taken lightly and we address some, but not all, of
these security concerns in Section~\ref{sec:security}.

  \item \textbf{Portability}

    Following security, portability of the analysis engines is the
next biggest concern. Due to the high cost of running computationally
expensive algorithms in the cloud, consumers can save money by testing
and developing algorithms locally and then moving to the cloud for
production analysis. Similarly, consumers may find it beneficial
to move from cloud to cloud to capitalize on lower computation prices.
To support this, clouds must have support for similar image formats as
each other and the testing/development environment. The issue of
portability is addressed in Section~\ref{sec:portability}

  \item \textbf{Dealing with Unstructured Data}

    Data collection is happening at rates much faster than it can be
properly stored in a meaningful structured manner, thus it is crucial
the data analysis platform supports an analytics engine that converts
unstructured data into structured data and combines it with existing
structured data. Section~\ref{sec:structuring} discusses the design
decisions taken to accommodate the need for structuring of data.

  \item \textbf{Ease of Use}

    Finally, the entire system should be relatively easy to use.
Although ease of use is subjective and hard to measure, we discuss the
design decisions and argue how the decisions increase the usability of the
platform and data analytics engines in Section~\ref{sec:ease}. In
general, systems are easier to use when presented with intuitive
graphical user interfaces and minimalistic configuration/command line
interaction.

\end{enumerate} 
