\subsection{Problem Statement}
\label{sec:problem}

Current open-sourced analytic packages are built for a few specific data
sets and data analysts must pick a platform that fits their data best. The
Institute for Next Generation IT Systems (ITng) wishes to provide,
maintain, and use a ``master image'' containing all such services in one
platform. Users will then be able to choose the services they need to fit
their data set and the environment will be set up with minimal
configuration and interaction.

In a data analysis engine, data goes through three major data 
transformation steps. \textit{Data Input}, \textit{In-depth Data Analysis},
and \textit{Presentation of Results}. For each one of these steps there are
many different tools and packages a consumer could use, each with their
own advantages based on the use case and the data set. This project aims
to set up an initial base platform for a data analytics engine, then build 
a data analysis package using this platform. This platform can then be 
expanded further by future developers to support other data analysis
packages.

The final deliverables of this project are an analytics cloud platform built
using OpenStack PackStack on a physical host in the Oscar Lab running Red
Hat Enterprise Linux 7.3 and a data analytics engine with the following
features: web crawling using Apache Nutch, storing unstructured data
with Apache Cassandra, indexing and structuring data with Solr/Lucene,
storing structured data with PostgreSQL, filtering data with Mortar and
visualizing data with Portrait. 
