\subsection{Milestones}
\label{sec:milestones}

The project requirements, and furthermore the system design, 
implementation, and testing are broken down into major milestones. These
milestones are then further divided into the individual tasks as described
in Section~\ref{sec:tasks} and assigned to team members in
Section~\ref{sec:distribution}. 

\begin{enumerate}
  \item \textbf{Obtain Access}

  This milestone includes coordinating with advisers to setup
    communication channels, sending public keys, and getting access to
    the environment from the advisers.

  \item \textbf{Obtain Requirements}

    This milestone involves all activity related to obtaining and
    refining project requirements, such as team meetings with the
    advisers, reading project specifications, and team only meeting
    attendance.

  \item \textbf{Initialize Environment}

    Initializing the environment involves configuring the host machine
    and installing OpenStack PackStack.

  \item \textbf{Connect to GPFS}

    Connect to GPFS refers to the configuration of the OpenStack
    deployment to use the GPFS as a back end for both Glance image
    storage and Nova VM back ends.

  \item \textbf{Initialize Analysis Node}

    Initializing the Analysis Node milestone includes creating a custom
    flavor for the instance to run as, setting up user accounts, and
    making a snapshot once configured.

  \item \textbf{Initialize Storage Node}

    Similarly to initializing the Analysis Node milestone, this
    milestone refers to the creation of a custom flavor, setting up user
    accounts, and finally creating a snapshot once configured.

  \item \textbf{VM Connectivity}

    This milestone refers to both allowing the VMs to communicate with
    each other, but also allowing VMs to access the Internet. This
    covers both firewall rule adjustments and network creation in
    OpenStack.

  \item \textbf{Install Dev Tools}

    This milestone is met when all development tools are installed on
    the development VM.

  \item \textbf{Install DB Tools}

    This milestone is met when all database tools are installed on the
    database VM.

  \item \textbf{Verification and Validation}

    This milestone refers to the testing and validation of each
    individual component in the two VMs, the testing and validation of
    each component interacting within the VMs, and finally the
    components between the VMs.

  \item \textbf{Documentation}

    This milestone refers to the writing of each and every section of
    the report.

  \item \textbf{Project Logistics}

    Finally this milestone refers the in-class progress reports, the
    final oral presentation, and the finalized report hand in.
\end{enumerate}
