\subsection{Functional Requirements}
\label{sec:func-reqs}

The cloud platform must provide the following (FR = Functional Requirement):
\begin{enumerate}[label=\textbf{FR-\arabic*}]
\item \textbf{Implemented on RHEL 7:} 

  The base operating system on the host and the operating system
  for the developer and data storage VMs must be Red Hat Enterprise
  Linux 7.
  
\item \textbf{Implemented in a cloud environment:}

  The analytics platform must be deployed as a cloud environment or
  an environment easily recreatable in a public cloud.

\item \textbf{Local cloud built using OpenStack:} 

  All guest VMs must run in an OpenStack deployment installed 
  locally on the supplied host machine. OpenStack will be deployed on
  the single machine using the OpenStack PackStack tool managed by
  RDO~\cite{rdo} to manage the deployment.


\item \textbf{Developer VM:}
  
  The platform must include one or more developer VMs with
  preinstalled packages for data analysis.

\item \textbf{Storage VM:}
  
  The platform must include one or more data storage VMs
  preconfigured to store structured and unstructured data.


\item \textbf{GPFS backed Deployment:}

  The analytics platform must use the IBM GPFS supplied by ITng to
  store images with Glance and as a back-end for running instances
  with Nova. 

\item \textbf{Developer VM must allow web scraping:} 

  The developer VM must have Apache Nutch 2.2.1 installed to 
  allow a data analyst to crawl the web for unstructured data.

\item \textbf{Storage VM must store structured and unstructured data:}
  
  The storage VM must have Apache Cassandra 2.2.8 installed to store
  unstructured data gathered from web crawling and PostgreSQL 9.2.1
  installed to store structured data.

\item \textbf{Developer VM must include a data indexer:}

  The developer VM must have Apache Solr 6.3.0 installed to index 
  unstructured data obtained from crawling the web

\item \textbf{Developer VM must allow data filtering:}

  The developer VM must have the Mortar web application to easily
  apply filters to unstructured data index in Solr.

\item \textbf{Developer VM must allow annotations on indexed data:}

  The developer VM must allow users to create and insert annotations 
  on indexed data to convert from unstructured to structured data. 
  Apache Ant 1.9.6, Apache UIMA 2.9.0, and Eclipse Workbench must be
  installed to support the creation and installation of annotations.

\item \textbf{Storage VM must allow for data import via CSV:}

  The storage VM must accept structured data in a CSV format from 
  the developer VM. Likewise, the developer VM must support exporting
  structured data in a CSV format from Solr to a PostgreSQL database.

\item \textbf{Developer VM must support visualization of data:}

  The developer VM must have Portrait installed to allow a user to
  view structured data stored in the PostgreSQL database.

\item \textbf{Access Control:}

  The platform must employ access control to VMs preventing the
  unauthorized access to virtual machines and the host machine.


\end{enumerate}
