\subsection{Limitations and Future Work}
\label{sec:limitations}

In this section we discuss the limitations of both our analytics cloud
platform and data analysis engine due to functionality we could not
complete and then end with discussion about future work, such as our
reach goals.

\subsubsection{Limitations}
Unfortunately we had one core goal that was not met in the implementation
of our analytics cloud platform. This goal was not met for a combination 
of reasons such as time constraints, lack of knowledge, and debugging
trouble. Here we describe the impact on our system by not implementing
this core feature.

During the installation of OpenStack we tried multiple times to configure
Cinder Volumes to use the GPFS just as we configured Nova and Glance.
Unfortunately, for reasons we believe were caused by an installation bug,
we ran out of time to continue trouble shooting and reinstalled OpenStack
to a consistent state and moved on to the implementation of the analysis
engine without it. The major drawback as result of not configuring Cinder
to use GPFS is the limited host disk size prevents us from having a
database machine with a minimum 500 GB of storage space. Given more time
we believe we could have tracked down the bug and reached this core
goal.

\subsubsection{Future Work}
In addition to the core functionality described in the project
abstract~\cite{abstract}, many reach goals were not met by our design
and we list them here as future work.

\begin{enumerate}
  \item \textbf{Data Provenance} Currently our system does not track how
user data is changed, who changed it, or when it was changed. We do
acknowledge the seriousness of data provenance a recommend it as a
priority for future work.
  \item \textbf{Auto-scaling} We installed base tools to support an
auto-scaling feature, however due to time constraints we left it
unimplemented. Future work that includes auto-scaling should also
explore the trade-offs between the time it takes to operate on a
particular data set and cost of the resources used.
  \item \textbf{MySQL vs PostgreSQL} Once again due to time constraints
we were unable to compare the usage of a MySQL database back end vs. a
PostgreSQL database back end to hold structured data. Assuming the
mortar and portrait tools support MySQL databases, this is straight
forward task that can be done by configuring a second database virtual
machine with MySQL and changing the environment to use it instead. We
leave this for future work.
  \item \textbf{AWS Environment} After the completion of all other reach
goals, we would have like to explore the ability to port our system to
Amazon Web Services. If this could be done, then users would be able to
test their data analysis engines locally and then port them to AWS to
take advantage of more resources. Once again this was left as future
work. 
\end{enumerate}
